Beta to Release Matching: Method Validation

### 2019-09-24 report_validation.Rmd
Adding paragraph noting hold-out covariates and their utility.

>>>>

The usage of a performance metrics hold-out set is not necessary, when applying the model across versions. However, [research has shown](https://metrics.mozilla.com/protected/cdowhygelund/beta_subset_release.html#covariate_selection) that optimal feature selection for statistical matching uses the effects (e.g., hold-out covariates) rather than the response (e.g., whether it is Beta or Release) typical of predictive modeling. Therefore, knowledge of the metrics of concern before matching occurs is key.
